Notes on conformal manifolds

### 2025-09-15 Draft_MLFlatDirections.tex
Abstract propostion

\begin{center}
\textbf{Abstract}
\end{center}

>>>>

\begin{abstract}
	We investigate the structure of conformal manifolds arising in the context of the AdS$_3$/CFT$_2$ correspondence, with a focus on continuous flat directions in the scalar potential of gauged supergravity. Starting from a consistent truncation of six-dimensional $N=(1,1)$ supergravity compactified on AdS$_3 \times S^3$, we restrict to a five-scalar subsector and search for flat directions around the AdS$_3 \times S^3$ vacuum. 
	Our approach combines numerical exploration and symbolic inference. We first employ gradient descent methods to efficiently sample the solution space and identify the dimensionality of the underlying manifold. The analysis reveals a connected three-dimensional family of solutions preserving the AdS$_3$ background. To obtain analytic relations, we develop a symbolic regression algorithm based on Annealed Importance Sampling (AIS) combined with Sequential Monte Carlo (SMC), well-suited to uncovering polynomial constraints in high-dimensional parameter spaces. 
	The algorithm reconstructs a set of polynomial relations projecting a five embedding set of coordinates onto the three-dimensional manifold, thereby providing an explicit analytic parametrization of the solutions. 
	This work demonstrates the potential of machine learning techniques to bypass the complexity of direct symbolic manipulation in supergravity and opens the way for systematic classifications of conformal manifolds in holographic theories.
\end{abstract}
